R Markdown for Reproducible Research

### 2019-01-25 paper.Rmd
add notes on code chunks, rstudio documentation, customized emails and git

Every code chunk has _many_ options. These are specified

@@

@@

@@

>>>>

Every code chunk has options that control its behavior. These are specified in
the header above the code chunk:

````
```{r my_chunk_name, my_option="one", my_other_option="two"}
r_code <- do_stuff(to_inputs)
```
````

While there are [_many_ such options](todo), some of the most ubiquitous are:

- `echo` - whether to "echo" the executed code in the output document
- `include` - whether to include output of the chunk in the output document
- `message` - whether to include messages from the chunk in the output document

Further, it is advisable to remember that the defaults can be set with code like:
```r
knitr::opts_chunk$set(echo = FALSE)
```

@@

RStudio has adopted R Markdown as the standard for some of its most important
communication. If you are interested in examples, we

- host our [company blog](todo) and [community blog](todo) using [blogdown](todo)
- write (most) [product documentation](https://docs.rstudio.com/) using [bookdown](todo)
- build [many](todo) [popular](todo) [websites](todo) using [pkgdown](todo)
- write presentations and papers like this one using R Markdown

We like to think that the sky is the limit when it comes to the reproducible
results that can be achieved using R Markdown, and are always excited to see
the very cool things that the open source community builds using this tool.

@@

While emails may not be very relevant to the _researcher's_ task, per se, they
are a common means of communication for many supportive functions. R Markdown
reports have what is called [_output metadata_](todo) that can be consumed by
external services. This, combined with packages like [`blastula`](todo) that
enable customized email bodies, can facilitate programmatically generating
reports, documents, or presentations that are programmatically delivered in a
customizable and personalizable fashion to the consumers of such content.

RStudio Connect is an example of a platform designed to leverage this tooling
for this end, and there are [several examples]() to explore if interested.

@@

Being able to reproduce a single version of one's research is fantastic... but
what if you could reproduce _every_ version of one's research? That is the sort
of magic that "Version Control" provides.

`git` is the most popular version control tool, followed by `subversion`. These
tools are oriented around software engineering and tracking / "diffing" changes
in source documents (mostly code) over time.

Since our research in this workflow is entirely driven by data along the highway
of code, it makes sense to spend some time getting used to these tools. If we
make version control a part of our process, we get reproducible research up to a
moment in time and easy auditability of code differences since R Markdown
consists of plaintext documents that are easily compared over time.

There are several helpful tutorials and books on the topic, principally [Happy
Git with R](todo), and even a built-in `git` pane within the RStudio IDE to simplify
some operations (todo).

![The RStudio IDE `git` pane with new commits and a modified paper](./img/git-ide.png)
